%!TEX root = ts.tex

\rSec0[scope]{Scope}

\pnum
This document describes requirements for implementations of an interface that computer programs written in the C++ programming language may use to invoke algorithms with concurrent execution. The algorithms described by this document are realizable across a broad class of computer architectures.

\pnum
{\cppstddocno} provide important context and specification for
this document. This document is written as a set of changes against that specification.  Instructions to modify or add paragraphs are written as
explicit instructions.  Modifications made directly to existing text from {\cppstddocno} use \added{underlining} to represent added text and \removed{strikethrough} to represent deleted text.

\pnum
This document is non-normative. Some of the functionality described by this document may be considered for standardization in a future version of C++, but it is not currently part of any C++ standard. Some of the functionality in this document may never be standardized, and other functionality may be standardized in a substantially changed form.

\pnum
The goal of this document is to build widespread existing practice for eventually adopting transactional memory in C++.

\rSec0[refs]{Normative references}

\pnum
The following referenced document is indispensable for the application of this document. For dated references, only the edition cited applies. For undated references, the latest edition of the referenced document (including any amendments) applies.

\begin{itemize}
\item {\cppstddocno}, \doccite{Programming Languages --- C++}
\end{itemize}

\pnum
ISO/IEC 14882:2020 is herein called the C++ Standard. References to clauses within the C++ Standard are written as ``\CppXref{defns.arbitrary.stream}''.


\rSec0[defs]{Terms and definitions}
\pnum
\indextext{definitions|(}%
No terms and definitions are listed in this document. ISO and IEC maintain
terminological databases for use in standardization at the following addresses:

\begin{itemize}
    \item IEC Electropedia: available at https://www.electropedia.org/
    \item ISO Online browsing platform: available at https://www.iso.org/obp
\end{itemize}

\rSec0[general]{General}

\rSec1[general.compliance]{Implementation compliance}
\pnum
Conformance requirements for this document are those defined in \CppXref{intro.compliance}, as applied to a merged document consisting of C++20 amended by this document.
\begin{note}
Conformance is defined in terms of the behavior of programs.
\end{note}

\rSec1[general.ack]{Acknowledgments}

This work is the result of a collaboration of researchers in industry and academia. We wish to thank the
original authors of this document, Michael Wong, Hans Boehm, and Michael Spear. We also wish to thank people
who made valuable contributions within and outside these groups, including Jens Maurer, and many others not named
here who contributed to the discussion.
